---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

Load library

```{r, message=FALSE}
library(tidyverse)
library(recipes)
```

## Loading and preprocessing the data

```{r}
activity <- read_csv("activity.zip", col_types = cols(date = col_date(format = "%Y-%m-%d"), 
                                                      steps = col_integer()), na = "NA")
```

```{r}
activity
```

## What is mean total number of steps taken per day?

Here's the histgram
```{r}
activity %>% group_by(date) %>% 
    ggplot(aes(steps)) + geom_histogram(bins = 40)
```

For mean and median
```{r}
activity %>% group_by(date) %>% 
    summarise(mean = mean(steps, na.rm = T),
              median = median(steps, na.rm = T))

```


## What is the average daily activity pattern?


Here's the line plot
```{r}
activity %>% group_by(interval) %>% 
    summarise( m_steps = mean(steps, na.rm = T)) %>% 
    ggplot(aes(interval, m_steps)) + geom_line()
```

The interval 835 has the maximum number of steps.
```{r}
activity %>% group_by(interval) %>% 
    summarise( m_steps = mean(steps, na.rm = T)) %>% 
    arrange(desc(m_steps)) %>% slice(1)
```
## Imputing missing values

From below, here are 2304 row contain NA. 
```{r}
activity %>% filter(is.na(steps) | is.na(interval) | is.na(date)) %>% 
    summarise(n_NA = n())
```

impute steps with mean, use floor values to keep it as integer.
```{r}
imp_fun <- function(dat){
    dat %>% recipe(~steps + date, data = .) %>% 
                 step_meanimpute(steps) %>% prep(retain = T) %>% 
                 juice()
}
nes <- activity %>% group_by(interval) %>% 
    nest() %>% mutate(data = map(data, imp_fun))
                        
imputed_df <- nes %>% unnest() %>% mutate(steps = as.integer(steps)) %>% arrange(date)

imputed_df
```

```{r}
imputed_df %>% group_by(date) %>% 
    ggplot(aes(steps)) + geom_histogram(bins = 40)
```
```{r}
imputed_df%>% group_by(date) %>% 
    summarise(mean = mean(steps, na.rm = T),
              median = median(steps, na.rm = T))
```
The result doesn't change much. Some days which are previous NA now have values.


## Are there differences in activity patterns between weekdays and weekends?


Here's the dataframe after adding the new factor variable.
```{r}
imp_fac <- imputed_df %>% mutate(wd = case_when(weekdays(date) %in% c("Saturday", "Sunday") ~ "Weekend",
                                     TRUE ~ "weekday")) %>% mutate(wd = factor(wd))
imp_fac
```
Here are the plots.
```{r}
imp_fac %>% group_by(wd,interval) %>% summarise(m_steps = mean(steps, na.rm = T)) %>% 
    ggplot(aes(x = interval, y =m_steps)) + geom_line() + facet_grid(wd~.) + ylab("number of steps")
```



















